A free/open-source Kazakh-Tatar machine translation system

### 2013-04-17 paper/paper.tex
cleaned up bit about past tense systems

> Past tense system

>>>>

The past tense systems of Kazakh and Tatar have a many-to-many correspondence.  At a basic level, Kazakh differentiates [±eyewitness]\footnote{``Eyewitness'' is a convenient term for this feature, though it may be better expressed as simply ``reliability of knowledge'' (which indeed often equates to whether the knowledge was acquired first-hand or not) in many cases.} (where [-eyewitness] is used for cases of both potentially unreliable information and newly discovered information) and [±recent] in the past tense, whereas Tatar has only three categories: eyewitness, non-eyewitness, and newly-acquired-information---all with no [±recent] distinction.  As an example of the many-to-many correspondence that this results in, Tatar has a single non-eyewitness past tense morpheme (\texttt{-GAн}) while Kazakh has a recent non-eyewitness past (\texttt{-IптI}) and a distant non-eyewitness past (\texttt{-GAн екен-}).  On the other hand, these two non-eyewitness past forms in Kazakh are used for both potentially unreliable information and newly acquired information, whereas in Tatar, non-eyewitness (\texttt{-GAн-}) and newly-acquired-information (\texttt{-GAн- икән}) past forms are distinguished.

Morphotactics of -GAн екен/икән
